---
title: "Submitting Data to the Herbarium EXAMPLE"
author: "Jasmine"
date: '2019-04-29'
output: html_document
---

specify some variables
```{r}
#bceause Country and Province state were not specified before in the Master list
ctry <- "Canada"
prov <- "British Columbia"

pid <- "PTM_CArbuscula"
```


Make sure you have these packages installed
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readxl)
library(tidyverse)
library(googlesheets)
library(here)
library(taxize)
```

load your data
```{r}
file <- "Master Collector Excel Templates_Kyra2019.xlsx"
s_num <- 2
row_skip <- 4
```

## Load in your spreadsheet with your PTM numbers
```{r}
original <- read_xlsx(here("./data/",file), sheet = s_num, skip = row_skip)

#removes rows that are not specimens (ie NA)
df_na <- filter(original, str_detect(original$`Collector Number`, "PTM"))
```

## Load in herbarium template
```{r}
collector_a <- read_xlsx("Master-Collector-Excel-Templates-20190429.xlsx",sheet = 2, skip = 4)
```


## Read in the master list
```{r}
library(googlesheets)
#library(googlesheets4) # future will be googlesheets4
#(ptm <- drive_get("PTM - Master List"))

#need to authenticate (see popup window)
mysheets <- gs_ls()

gs_master <- gs_title("PTM - Master List")

#gets the data
gs_ptm<- gs_read(gs_master)

#cleans up columns
colnames(gs_ptm) <- gs_ptm[1,]
new <- gs_ptm[-c(1,2),]
```

## Select the rows
```{r}
df <- new %>% 
  mutate(num = paste0("PTM",`PTM#`)) %>% 
  filter(num %in% df_na$`Collector Number`)
```

### Figure out which name to use
```{r}
df_nm <- df %>% 
  mutate(choice = if_else(is.na(df$`Final determination`),
                      df$`Determination in the field`,
                      df$`Final determination`),
         gs = choice) %>% 
  separate(choice, c("Genus","Species"), " ")

# check
names <- cbind(df$`Final determination`, df$`Determination in the field`, df$`genetic match/notes`)
```

### Phylum Class Family
- !!! fix species
- BOLD is pretty reliable but still has mistakes on some obscure species
- only run if there isn't any phylum data
- can we use the herbarium data base?

!!! need to see if you can get authorship
```{r}
higher <- classification(df_nm$Genus, db= "bold")

#itis <- classification(df_nm$Genus, db="itis")
#itis_2 <- classification(df_nm$gs, db="itis")

empty <- collector_a[FALSE,]

for(i in 1:length(higher)) {
  if(!is.na(higher[i])) {
    species <- higher[[i]]
    rect <- c(species$name)
    names(rect) <- c(species$rank)

    empty <- empty %>%
      add_row(Phylum = rect["phylum"],
              Class = rect["class"],
              Genus = rect["genus"])
  }
  else{empty <- empty %>%  add_row(Phylum = NA)}
}
```

```{r}
meta <- df_nm %>%
  mutate(Herbarium = "UBC",
         LabelQty = 1,
         Qualifier = "") %>% 
  cbind(empty$Phylum,empty$Class,empty$Genus)

## select columns
herb <- meta %>% 
  select(`PTM#`, Herbarium, LabelQty, `empty$Phylum`, `empty$Class`, Genus,Qualifier, Species, #Species Authonr
         Locality,Latitude, Longitude, Habitat, Depth, `Reproductive Status`, `Date Collected`, `Main Collector`, `PTM#`,Determiners, DeterminationDate, Notes )
```

```{r}
meta_k <- df_nm %>%
    separate(Locality,c('smaller','larger'), sep = ",") %>% 
  mutate(Herbarium = "UBC",
         LabelQty = 1,
         Qualifier = "",
         Country = ctry,
         ProvinceState = prov,
         Coralline = "Yes",
         Location = paste(larger, ",", smaller),
         Collectornum = paste0("PTM",`PTM#`),
         ProjectID = pid) %>% 
  cbind(empty$Phylum,empty$Class,empty$Genus)


kyra <- meta_k %>% 
  select( Herbarium, LabelQty, `empty$Phylum`, `empty$Class`, Genus,Qualifier, Species, #Species Authonr
         Country, ProvinceState, Location,Latitude, Longitude, Habitat, Depth, `Reproductive Status`, `Date Collected`, `Main Collector`,`Other collectors`, Collectornum, Determiners, DeterminationDate, Notes, Coralline)
```

```{r}
write_csv(kyra,"output/2019Sept24_KyraCoralline.csv", na = "")
```

